---
title: "Paper Flow"
author: "Danilo Sarti"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Paper Flow}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r}
library(frons)
```

# Simulating BLUEs

```{r}
sim_blues=sim_blue_model(pars = list(I = 4,J=3,Z=3,R=2,u_treat=0,sigma_treat=1,u_gen=0,
                                    sigma_gen=1,u_block=0,sigma_block=1,u_pb=0,sigma_pb=1, u_gp=0, sigma_gp=1,u_mean=0,sigma_mean=1,u_epsilon=0, sigma_epsilon=1
))
head(sim_blues$test_df)[1:3,1:4]
```


# Simulating from Model 1 


## setting global parameters required by the model 

```{r}
# setting global parameters
I=2#number of genotypes
J=3 #number of environments 
K=10 # envirnmental covariates
# simulating a matrix of markers w_a
#WA= markes columns individual rows 0,1,2
#0- AA, 1-Aa, 2aa.
n_markers=600
marker_label=sprintf("marker_%s",seq(1:n_markers))
markers_expression=c(0,1,2)
data_expression=sample(markers_expression,n_markers*I,replace = TRUE)
w_a=matrix(data_expression,nrow=I,ncol = n_markers)
colnames(w_a)=marker_label
rownames(w_a)=gen_label=sprintf("genotype_%s",seq(1:I))
# we must calculate now the $2 \sum_{l}^{n} p_{l}\left(1-p_{l}\right)$


## generate a matrix of environmental relationship
n_env_cov=3
env_cov_label=sprintf("env_cov_%s",seq(1:n_env_cov))
env_lab=sprintf("environment_%s",seq(1:J))
envs_expression=rnorm(100)
data_env=sample(envs_expression,n_env_cov*J,replace = TRUE)
x_env=matrix(data_env,nrow=J,ncol = n_env_cov)
colnames(x_env)=env_cov_label
rownames(x_env)=env_lab

u_mean=100
sigma_mean=20
sigma_ag=1
u_env=0
sigma_env=1 
u_epsilon=0 
sigma_epsilon=1
u_gen=0
u_mean=0
sigma_ge=1
u_ge=0
sigma_w=1
u_w=0
sigma_aw=1
```



```{r}
sim_m1=sim_m1(pars=list(w_a=w_a,u_mean=0,sigma_mean=1, sigma_a=1,u_env=0,sigma_env=1, u_epsilon=0, sigma_epsilon=1,J=3,I=2,u_gen=1))

head(sim_m1$test_df)
```

# Simulating from model 2

```{r}
m_2=sim_m2(pars=list(I=I,J=J,w_a=w_a,sigma_a=sigma_ag,u_mean=u_mean,sigma_mean=sigma_mean,u_env=u_env,sigma_env=sigma_env, u_gen=u_gen,sigma_env=sigma_env,sigma_ge=sigma_ge,u_ge=u_ge,sigma_ge=sigma_ge,u_epsilon=u_epsilon,sigma_epsilon=sigma_epsilon))
head(m_2$test_df)
```

# Simulating from Model 3:

```{r}
m_3=sim_m3(pars=list(I=I,J=J,K=K,w_a=w_a,sigma_a=sigma_ag,u_mean=u_mean,sigma_mean=sigma_mean,u_env=u_env,sigma_env=sigma_env, u_gen=u_gen,sigma_env=sigma_env,u_epsilon=u_epsilon,sigma_epsilon=sigma_epsilon, x_env=x_env,sigma_w=sigma_w,u_w=u_w))
head(m_3$test_df)
```

# Simulating from Model 4:


```{r}
m_4=sim_m4(pars=list(I=I,J=J,K=K,w_a=w_a,sigma_a=sigma_ag,u_mean=u_mean,sigma_mean=sigma_mean,u_env=u_env,sigma_env=sigma_env, u_gen=u_gen,sigma_env=sigma_env,u_epsilon=u_epsilon,sigma_epsilon=sigma_epsilon, x_env=x_env,sigma_w=sigma_w,u_w=u_w,sigma_ge=sigma_ge,u_ge=u_ge))
head(m_4$test_df)
```

# Simulating from Model 5:

```{r}
m_5=sim_m5(pars=list(I=I,J=J,K=K,w_a=w_a,sigma_a=sigma_ag,u_mean=u_mean,sigma_mean=sigma_mean,u_env=u_env,sigma_env=sigma_env, u_gen=u_gen,sigma_env=sigma_env,u_epsilon=u_epsilon,sigma_epsilon=sigma_epsilon, x_env=x_env,sigma_w=sigma_w,u_w=u_w,sigma_ge=sigma_ge,u_ge=u_ge,sigma_aw=sigma_aw))

head(m_5$test_df)
```


# To build large simulations 

## create a dataframe containing information about the scenarios 

This procedure can take long to be made. Consider using the data sets contained in the data folder. 

```{r}
n_genotypes=c(200,500)
n_env<-c(10,20)
k_envs=c(100)
n_markers=c(1500,5000)
u_mean=c(5,10)
sigma_mean=c(1.5,3)
#used for estimating g_i multiplied by G_a matrix
sigma_a=c(2,5)
u_env=c(2,3)
sigma_env=1.5 
u_epsilon=0 
sigma_epsilon=1
u_gen=3
sigma_ge=c(1,2)
u_ge=c(1,2)
sigma_w=c(0.5,0.9)
u_w=c(2,5)
sigma_aw=1

df_scenarios=expand.grid(n_genotypes=n_genotypes,
                         n_env=n_env,
                         k_envs=k_envs,
                         u_mean=u_mean,
                         sigma_mean=sigma_mean,
                         #used for estimating g_i multiplied by G_a matrix
                         sigma_a=sigma_a,
                         u_env=u_env,
                         sigma_env=sigma_env, 
                         u_epsilon=u_epsilon,
                         sigma_epsilon= sigma_epsilon,
                         u_gen=u_gen,
                        
                         sigma_ge=sigma_ge,
                         u_ge= u_ge,
                         sigma_w=sigma_w,
                         u_w=u_w,
                         sigma_aw=sigma_aw,
                         n_markers=n_markers
)
dim(df_scenarios)



```


```{r}
# for ( i in 1:nrow(df_scenarios)){
#   i=1
#   n_genotypes=df_scenarios[i,1]
#   n_env<-df_scenarios[i,2]
#   k_envs=df_scenarios[i,3]
#   I=n_genotypes
#   J=n_env
#   K=k_envs
#   u_mean=df_scenarios[i,4]
#   sigma_mean=df_scenarios[i,5]
# 
#   sigma_a=df_scenarios[i,6]
#   u_env=df_scenarios[i,7]
#   sigma_env=df_scenarios[i,8]
#   u_epsilon=df_scenarios[i,9] 
#   sigma_epsilon=df_scenarios[i,10]
#   u_gen=df_scenarios[i,11]
#   
#   sigma_ge=df_scenarios[i,12]
#   u_ge=df_scenarios[i,13]
#   sigma_w=df_scenarios[i,14]
#   u_w=df_scenarios[i,15]
#   sigma_aw=df_scenarios[i,16]
#   n_markers=df_scenarios[i,17]
#   
# # generate matrix w_a
#   marker_label=sprintf("marker_%s",seq(1:n_markers))
#   markers_expression=c(0,1,2)
#   data_expression=sample(markers_expression,n_markers*n_genotypes,replace = TRUE)
#   w_a=matrix(data_expression,nrow=n_genotypes,ncol = n_markers)
#   colnames(w_a)=marker_label
#   rownames(w_a)=gen_label=sprintf("genotype_%s",seq(1:n_genotypes))
# 
# #generate environment kernels 
#   env_cov_label=sprintf("env_cov_%s",seq(1:k_envs))
#   env_lab=sprintf("environment_%s",seq(1:J))
#   envs_expression=rnorm(100)
#   data_env=sample(envs_expression,k_envs*J,replace = TRUE)
#   x_env=matrix(data_env,nrow=J,ncol = k_envs)
#   colnames(x_env)=env_cov_label
#   rownames(x_env)=env_lab
# 
# # generating data 
#   #################################################
#   m_1=sim_m1(pars=list(w_a=w_a,u_mean=u_mean,sigma_mean=sigma_mean, sigma_a=sigma_a,u_env=u_env,sigma_env=sigma_env, u_epsilon=u_epsilon, sigma_epsilon=sigma_epsilon,J=J,I=I,u_gen=u_gen))
#   ##################################################
#   m_2=sim_m2(pars=list(I=I,J=J,w_a=w_a,sigma_a=sigma_a,u_mean=u_mean,sigma_mean=sigma_mean,u_env=u_env,sigma_env=sigma_env, u_gen=u_gen,sigma_env=sigma_env,sigma_ge=sigma_ge,u_ge=u_ge,sigma_ge=sigma_ge,u_epsilon=u_epsilon,sigma_epsilon=sigma_epsilon))
#   
#   ##################################################
#   m_3=sim_m3(pars=list(I=I,J=J,K=K,w_a=w_a,sigma_a=sigma_a,u_mean=u_mean,sigma_mean=sigma_mean,u_env=u_env,sigma_env=sigma_env, u_gen=u_gen,sigma_env=sigma_env,u_epsilon=u_epsilon,sigma_epsilon=sigma_epsilon, x_env=x_env,sigma_w=sigma_w,u_w=u_w))
#   
#   #####################################
#   m_4=sim_m4(pars=list(I=I,J=J,K=K,w_a=w_a,sigma_a=sigma_a,u_mean=u_mean,sigma_mean=sigma_mean,u_env=u_env,sigma_env=sigma_env, u_gen=u_gen,sigma_env=sigma_env,u_epsilon=u_epsilon,sigma_epsilon=sigma_epsilon, x_env=x_env,sigma_w=sigma_w,u_w=u_w,sigma_ge=sigma_ge,u_ge=u_ge))
#   ####################################
#   m_5=sim_m5(pars=list(I=I,J=K,K=K,w_a=w_a,sigma_a=sigma_a,u_mean=u_mean,sigma_mean=sigma_mean,u_env=u_env,sigma_env=sigma_env, u_gen=u_gen,sigma_env=sigma_env,u_epsilon=u_epsilon,sigma_epsilon=sigma_epsilon, x_env=x_env,sigma_w=sigma_w,u_w=u_w,sigma_ge=sigma_ge,u_ge=u_ge,sigma_aw=sigma_aw))
#   ## Insert here how to save the files generated. 
# }
```

